{\bf Intrusion Detection using Parzen-Windows on Provenance Graph Statistics}

### 2013-12-10 writeup/paper-final.tex
Outline

>>>>

\subsection{Outline}
In Section 2 we discuss work related to both provenance collection and intrusion detection. In Section 3 we detail our initial exploratory experiments on small data sets, determining which provenance graph features we wanted to explore further in designing our approach, as well as the implementation details of our initial experimental setup. In Section 4, we discuss the setup, results, and findings of our main experiment, in which we tested our approach on existing large intrusion detection data sets. In Section 5 we discuss future work and directions that this project has motivated, and in Section 6 we conclude.
